|

### 2020-12-09 01-Chp1-Introduction.Rmd
Double-saving

>>>>

## Additional ideas

* Explore difference/similarities between the published and unpublished literature, potentially formally, using funnel plots and also by following up preprints to see if they are eventually published. Limit to the date we ran the original search and see if any study included in the study had not been published by the time the review was finished. 
* Compare and contrast the codes used to find the AzD cases in the previous study and in this study, potentially with a view to contrasting misclassification between the two.

### 2020-12-09 04-Chp2-Systematic-Review.Rmd
Double-saving

@@

How to interpret agreement co-efficients is widely debated. Here we use guidelines based on a stricter interpreation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).

Gwet's AC1 is calculated using the following:

@@

```{r gwet-table, echo = FALSE}
```

```{r agreement-table-inter, echo = FALSE}
```

```{r agreement-table-intra, echo = FALSE}
```

@@

```{r prisma-flow, echo = FALSE, warning=FALSE, message=FALSE, fig.cap="PRISMA flow diagram, detailing the movement of studies through the systematic review.", out.width="100%"}
```

>>>>

## Lay summary

@@

How to interpret agreement co-efficients is widely debated. Here we use guidelines based on a stricter interpreation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:gwettable).

In a two by two table with cells A, B, C and D, Gwet's AC1 is calculated using the following:

$$AC1 = \frac{p-e(\gamma)}{1-e(\gamma)}$$
Here, $p = \frac{A+D}{N}$ and $e(\gamma)$ is the chance agreement between raters, given as $2q(1-q)$, where $q = \frac{(A+C)+(A+B)}{2N}$

@@

```{r agreementtableinter, echo = FALSE}
```

```{r agreementtableintra, echo = FALSE}
```

@@

### 2020-12-09 05-Ch3-CPRD-Analysis.Rmd
Double-saving

Note: this will be harder for things that are not dichotmous and can go up as well as down. Examples include total cholesterol and BMI, which can go up as well as down.

@@

However, this is not the case. Baseline cholesterol level are predicted to be a poorer instrument for than QRISK2 score,[@hippisley-cox2008] which estimates a patients' 10-year risk of a cardiovascular event. Current NICE guidelines state that those with a QRISK score of 10% or higher, and in whom lifestyle modifcation is ineffective/inappropriate, should recieved a lipid regulation agent. However, this analysis could not find any effect of QRISK2 scores on statins precription levels at 6 months. [Need to cite Lauren's eventual paper here focusing on QRISK2, but also display a RD analysis of TC/LDL-c levels here on statins at 6 months. Need also to check, as Lauren mentioned she found some evidence that there is a relationship in practices that acutally did what they should.]

As expected, in a confirmatory analysis using lipid levels, there was no association between <span color="red">the most recent total cholesterol or LDL-cholesterol reading in the CPRD and the treatment, incdicating that adjusting for this variable was not required. *</span>

>>>>

Note: this will be harder for things that are not dichotomous and can go up as well as down. Examples include total cholesterol and BMI, which can go up as well as down.

@@

However, this is not the case. Baseline cholesterol level are predicted to be a poorer instrument for than QRISK2 score,[@hippisley-cox2008] which estimates a patients' 10-year risk of a cardiovascular event. Current NICE guidelines state that those with a QRISK score of 10% or higher, and in whom lifestyle modifcation is ineffective/inappropriate, should received a lipid regulation agent. However, this analysis could not find any effect of QRISK2 scores on statins precription levels at 6 months. [Need to cite Lauren's eventual paper here focusing on QRISK2, but also display a RD analysis of TC/LDL-c levels here on statins at 6 months. Need also to check, as Lauren mentioned she found some evidence that there is a relationship in practices that actually did what they should.]

As expected, in a confirmatory analysis using lipid levels, there was no association between *the most recent total cholesterol or LDL-cholesterol reading in the CPRD and the treatment, indicating that adjusting for this variable was not required.*

### Replicating the analysis

**Comparing and contrasting between different studies is particularly difficult** because of the impact that the use of differnet code list can have on the analysis [@wilkinson2018a; @mcguinness2019c]

### 2020-12-09 front-and-back-matter/99-appendices.Rmd
Double-saving

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
  bookdown::html_document2: default
  bookdown::pdf_document2:
    template: templates/brief_template.tex
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:sys-rev-tools-quote)'}
Why are open source statistical programming  
languages the best?

Because they R.
```
(ref:sys-rev-tools-quote) --- Bealy, 2013 [@bealy2013]

# Creating new systematic review tools in R {#sys-rev-tools-heading}
\minitoc <!-- this will include a mini table of contents-->

```{r setup, include=FALSE}
source("R/doc_options.R")
```

<!----------------------------------------------------------------------------->

## Background

Developing new tools for facilitating evidence synthesis will benefit patients by speeding up the speed with which systematic reviews are produced. A recent study put the mean duration of a systematic review project, from date of registration to date of publication is 67.3 weeks.[@borah2017] A large proportion of this time will be spent on manual tasks such as title and abstract screening, - therefore, efforts to increase the efficiency of the process should focus on process that can be automated.

Below I introduce two new R packages created to faciliate some aspects of the systematic review process.

@@

<!----------------------------------------------------------------------------->
## Searching for health-related preprints with `medrxivr`

Searching pre-print repositories is becoming an increasingly important part of a systematic review. Preprints - unpublished versions of manuscripts, frequently uploaded to a repository at the same time they are submitted to a journal for peer review - represent an important source of grey literature.

However, while several of the main repositories (e.g. arXiv, bioRxiv) have existing methods by which records can be searched and downloaded en masse,^[https://arxiv.org/help/api] this is not true for medRxiv, a repository launched in June 2019 to host preprints in the medical, clinical, and related health sciences.

At present, medRxiv allows only simple search queries, as opposed to the often complex Boolean logic that information specialists use to query other major databases. Additionally, record metadata (titles/abstracts/author lists) must be accessed individually, rather than in batches, meaning that downloading relevant records for title and abstract screening a time consuming task.

This source of information is particularly important to this thesis, in that one of the primary types of evidence that I planned to use in the triangulation exercise (Mendelian randomization (MR)) is still developing and many MR studies that look at the clinical question that this project aims to investigate are posted as preprints on the bioRxiv, and more recently medRxiv, preprint servers. Being able to systematically search these records for the purpose of the systematic review described in Chapter \@(ref:sys-rev-heading) was a necessity. In light of the above, the `medrxivr` R package was created in order to facilitate the searching of this data source.

Early versions of the tool

To install `medrxivr` from CRAN:

```{r, eval = FALSE}
install.packages("medrxivr")
```

To install the development version from GitHub:

```{r, eval = FALSE}
devtools::install_github("ropensci/medrxivr")
```

### Methods

The `medrxivr` project is split into two parts:

* A webscraper that runs once a day which collects and cleans new records uploaded to medRxiv, and adds them to a machine readable database.
* A lightweight R package that provides an interface for this database, allowing users to search for relevant records, and easily retieve the associated full tex PDFs.

The webscraper is a straightforward R script built in R using `rvest` and a range of text processing packages[@wickham2019; @wickham2019a; @wickham2020]. To quickly illustrate the process, the code to retrieve the total number of records on medRxiv is included below:

```{r,eval=FALSE}

# Perform a search for "*" (defined by %252A), which acts as a wildcard  
# This approach will capture all records
url <- "https://www.medrxiv.org/search/%252A"

# Read the HTML from this link
page <- read_html(url)

# Extract the text (html_text()) value of the CSS node of interest, in this
# case, the "#page-title" node

results <- page %>%
  html_nodes("#page-title") %>%
  html_text()

# Remove any commas from the results (e.g. 1,500 become 1500)
results <- gsub(",","",results)

# Convert it from a character string to a numeric
results <- as.numeric(word(results))

Using Windows Task Scheduler,[@zotero-880] the script is scheduled to automatically run every morning, adding new records uploaded to medRxiv since the last run of the webscraper to a local comma-seperated-values (CSV) file. Following a quality control pipeline, which checks the completeness of the new records and ensures that all records have been captured, the updated dataset is automatically uploaded to a cloud server and immediately becomes available to the `medrxivr` package functions.

The functions in the `medrxivr` package then facilitate users in working with this dataset. There are two main functions and a helper function:

* `mx_search()` [main]: Enables users to search the medrxivr data dump, using regular expressions and boolean logic.

```{r, eval = FALSE}
topic1  <- c("dementia","vascular","alzheimer's")  # Combined with OR
topic2  <- c("lipids","statins","cholesterol")     # Combined with OR

myquery <- list(topic1, topic2)                    # Combined with AND

results <- mx_search(myquery)
```

* `mx_download()` [main]: Takes the output from `mx_search()` and retrieves the full text PDF for each record, saving it to a folder specified by the user.

```{r, eval = FALSE}
mx_download(results,        # Object returned by mx_search
            "pdf/")         # Directory to save PDFs to 
```

* `mx_crosscheck()` [helper]: Provides information on the version of the data dump that the user is searching, and checks whether any new records have been uploaded to medRxiv since the last run of the webscraper.

```{r, eval = FALSE}
mx_crosscheck()

## Using medRxiv snapshot - 2020-03-04 10:55
## No new records added to medRxiv since last snapshot.
```

## Export

One of the key

## Data visualisation and reporter functions

**TBC**

The tool has be well received by the community, and several use cases have been reported. However, several other use cases have emerged for the tool. It has been used to visalise the growing number of preprints related to the 2019 coronavirus outbreak ^[https://twitter.com/L_Brierley/status/1233109086444695553], etc, etc

Following peer-review, it has been onboarded into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web", and an associated article published in the Journal of Open Source Software.

A short paper describing the tool has been published in the Journal of Open Source Software following formal peer-review of the package and associated documentation and tutorials as part of the rOpenSci onboarding process. The entire review discussion can be viewed online.^[https://github.com/ropensci/software-review/issues/380]

The tool has been used reasonably widely, included in the systematic reviews, but also to extract data to facilitate the compare the behavior of researchers under two different journal policies by comparing the preprint paper with the published journal paper.

Feedback from the systematic review community has been positive.

### Package infrastructure

The `medrxvir` package was written in R using RStudio, and followed development best practices, including complete and information documentation, a robust unit testing framework (99% of all code lines within the package are formally tested under this framework) across multiple platforms including Windows, MacOS, and Linux, and in-depth code review by two experienced reviewers.

The medRxiv snapshot is taken every morning using GitHub Actions, an automated system fo repetitive tasks.

## Shiny app

Part of the key theme of accessibility meant creating a web-application that l

<!----------------------------------------------------------------------------->
## Dicussion

Packaging and sharing R scripts should be a fundamental part of evidence synthesis process. [EXPAND]

As

By implementing the tools described above as both as an R package and a `Shiny` web app, the functionality is available to evidence synthesists with varying levels of ability in R. These tools serve as an example of the advantages of “packaging” the R scripts that evidence synthesists often create for personal use.[@wickham2015r] In the case of `robvis`, it is likely that several other evidence synthesists have written scripts to produce similar risk-of-bias plots to those presented here - in fact, in the course of its development, I identified one other research group that has done so. This duplication of time and effort is inefficient, and creating and sharing well-documented R packages represents one way to reduce this inefficiency. Taking this approach one step further, `Shiny` apps represent a straightforward way to provide a user-friendly GUI for a newly created R package within a very short timeframe, expanding the potential pool of users of the package to anyone with an internet connection.

Creating a package using R has a number of particular advantages. R provides access to a range of powerful tools including the `ggplot` infrastructure as demonstrated above, and RMarkdown, which enables creation of documents that can be rendered in a range of formats such as PDF, HTML, or Word.[@xie2018r] Furthermore, and focusing specifically on evidence synthesis, building new tools as packages in R allows for easy integration with the range of existing evidence synthesis packages. Recently, the `metaverse` project,[@variousauthors2020] of which `robvis` and `medrivr` are a part, has begun to curate a collection of R packages that cover different aspects of the systematic review and meta-analysis process which, when taken together, form a coherent end-to-end open-source alternative to commercial offerings such as Covidence or Review Manager. Key offerings in this suite of packages include litsearcher, which facilitates systematic search strategy development, revtools, a package for managing the review process and performing title and abstract screening, metaDigitise, a package for automatic extraction of data from figures in research papers, and metafor, a package for conducting meta-analyses in R.[@grames2019automated; @metaforref; @pick2018; @westgate2019revtools]

<!----------------------------------------------------------------------------->
## Summary

* In this Chapter, I have introduced two new tools for facilitating evidence syntheses: `robvis`, a tool for producing publication quality risk of bias assessments, and `medrxivr`, a tool for performing complex searches in the medRxiv preprint repository.

* I have outlined the motivation for developing these tools in relation to this thesis - more specifically, that they were used extensively to the conduct the comprehensive systematic review described in Chapter \@ref(sys-rev-heading)

* The impact of these packages to date, their place in the broader evidence synthesis in R ecosystem, and a roadmap for their future development has been discussed.

>>>>

`r if(knitr:::is_latex_output()) '\\startappendices'`

`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`

<!-- If you feel it necessary to include an appendix, it goes here. The first appendix should include the commands above. -->

# By Chapter

## Chapter 1

## Chapter 2

# Other Appendix

@@
